```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>"
)
source("../R/.common.R")

makeTable <- function(files){
    referenceFile <- files[grepl("parLapply", files)]
    otherFiles <- files[!grepl("parLapply", files)]
    timeTable <- readRDS(referenceFile)
    for(i in otherFiles){
        timeTable <- rbind(timeTable, readRDS(i))
    }
    
    timeTable <- timeTable[c(which(timeTable$source == timeTable$source[1]),
                             which(timeTable$source != timeTable$source[1])
    ),]
    
    timeTable$performance <- round(timeTable$time[1]/timeTable$time * 100, 2)
    name <- colnames(timeTable)
    name[name == "time"] <- "time(sec)"
    name[name == "performance"] <- "performance relative to baseline(%)"
    
    
    knitr::kable(timeTable, format = "markdown",
                 col.names = name)
}
```
# Introduction
This is a benchmark for the popular parallel packages `parallel`, `foreach` and `BiocParallel`. The source code for generating the benchmark result is available at the branch `source`.


# Overhead benchmark
This benchmark measures the overhead of the parallel functions. The function being evaluated is equivalent to
```{r, eval=FALSE}
lapply(1:n, function(x) runif(1))
```
where n=`r nOverhead`. All parallel functions use its default setting. Below is the table for the time consumption. 16 workers are used for each cluster(Note that the host may not have 16 CPUs)
```{r, echo=FALSE}
files <- list.files("../results/overhead", full.names = TRUE)
makeTable(files)
```


# CPU intensive benchmark
The function being evaluated is equivalent to
```{r, eval=FALSE}
lapply(1:n, function(x) {
    m <- 5000L
    value <- 0
    for(i in 1:m){
        value <- value + sum(sample(1:m, m))
    }
    value
})
```
where n=`r nCpu`. All parallel functions use its default setting.

```{r, echo=FALSE}
files <- list.files("../results/cpu", full.names = TRUE)
makeTable(files)
```

# BiocParallel benchmark history
## Overhead
```{r, include = FALSE}
readFileData <- function(files){
    data <- readRDS(files[1])
    for(i in files[-1]){
        data <- rbind(data, readRDS(i))
    }
    data
}
makePlot <- function(curData){
    idx <- sapply(curData$version, function(x) {
        sum(
            sapply(curData$version, function(y) compareVersion(x, y)) <=0
        )
    }
    )
    time <- curData$time[order(idx)]
    label <- curData$version[order(idx)]
    plot(seq_along(idx), time, type = "b", pch = 19, 
         col = "blue", xlab = "version", ylab = "secs", 
         ylim = c(0,max(time)), xaxt="n")
    axis(side=1, at=seq_along(idx), labels = label, las=2)
}
```


```{r}
files <- list.files("../results/history", full.names = TRUE)
overheadFiles <- files[grepl(".+BiocParallel-overhead-", files)]
overHeadData <- readFileData(overheadFiles)
for(backend in overHeadData$backend){
curData <- overHeadData[overHeadData$backend == backend,]
makePlot(curData)
}
```

## CPU intensive
```{r}
overheadFiles <- files[grepl(".+BiocParallel-cpu-", files)]
overHeadData <- readFileData(overheadFiles)
for(backend in overHeadData$backend){
curData <- overHeadData[overHeadData$backend == backend,]
makePlot(curData)
}
```

## Host machine specification
```{r}
benchmarkme::get_cpu()
benchmarkme::get_ram()
```

